Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-07-08 conclusion.tex
Added a piece (Please check that we are still at 10 pages)

The 52M core hours used by ATLAS, via PanDA, is over 2\% of the total
utilization on Titan over the same period, bringing the time-averaged
utilization of Titan to be consistently upwards of 90\%. Given that the
 average utilization of most other leadership class machines is less
(e.g., NSF's flagship Blue Waters the average utilization fluctuates between
60--80\% (see XDMoD\cite{bw-sucks})) there is ample headroom for similar
approaches elsewhere. These unprecedented efficiency gains aside, this work
is just a starting point towards more effective operational models for future
leadership and online analytical platforms~\cite{foap-url}. These platforms
will have to support ever increasing complex workloads with varying models
for dynamic resource federation.

>>>>

The 52M core hours used by ATLAS, via PanDA, is over 2\% of the total
utilization on Titan over the same period, bringing the time-averaged
utilization of Titan to be consistently upwards of 90\%. Given that the
 average utilization of most other leadership class machines is less
(e.g., NSF's flagship Blue Waters the average utilization fluctuates between
60--80\% (see XDMoD\cite{bw-sucks})) there is ample headroom for similar
approaches elsewhere. These unprecedented efficiency gains aside, this work
is just a starting point towards more effective operational models for future
leadership and online analytical platforms~\cite{foap-url}. These platforms
will have to support ever increasing complex workloads with varying models
for dynamic resource federation.
The development of NGE is looking forward to deal with these challenges by providing an abstraction layer for HPC resources together with a set of APIs for the coordination and fast deployment of heterogeneous workloads.  In this paper, we provided the results of a preliminary testing of the NGE. The testing pointed out the robustness of NGE at handling an high number of tasks and worker nodes by mantaining an overhead that grows linearly with the number of tasks.
